Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-12-13 article.qmd
Add mention to PyPI

Modular code architecture makes code reusable, extensible, and easier to maintain.
Therefore, we split the code to define and simulate reaction systems into three Python packages:
symbolite, to create symbolic expressions;
poincaré, to define dynamical systems;
and simbio, to define reaction systems and interface with systems biology standards such as SBML.

Symbolite is a lightweight symbolics package to create algebraic mathematical expressions.
Symbolite expressions can be inspected and compiled to various backends.
Currently, we have implementations for
NumPy [@harrisArrayProgrammingNumPy2020];
Numba [@lamNumbaLLVMbasedPython2015], a Just-in-Time (JIT) compiler to LLVM;
SymPy [@meurerSymPySymbolicComputing2017], a library for symbolic mathematics;
and JAX [@jax2018github], a library that support automatic differentiation
and compilation to GPUs and TPUs.
Symbolite is designed to facilitate the easy integration of new backends. The source code, documentation to install and use these packages and tutorials are available at the `github page link`.

>>>>

Modular code architecture makes code reusable, extensible, and easier to maintain.
Therefore, we split the code to define and simulate reaction systems into three Python packages:
symbolite, to create symbolic expressions;
poincaré, to define dynamical systems;
and simbio, to define reaction systems and interface with systems biology standards such as SBML.
These are pure Python packages with standard dependencies from the PyData scientific stack such as NumPy [@harrisArrayProgrammingNumPy2020] and pandas [@mckinneyDataStructuresStatistical2010].
They are published in PyPI (the Python Package Index),
where links to the source code and documentation hosted in GitHub can be found,
and can be easily installed with `pip install <package_name>`.

Symbolite is a lightweight symbolics package to create algebraic mathematical expressions.
Symbolite expressions can be inspected and compiled to various backends.
Currently, we have implementations for
NumPy [@harrisArrayProgrammingNumPy2020];
Numba [@lamNumbaLLVMbasedPython2015], a Just-in-Time (JIT) compiler to LLVM;
SymPy [@meurerSymPySymbolicComputing2017], a library for symbolic mathematics;
and JAX [@jax2018github], a library that support automatic differentiation
and compilation to GPUs and TPUs.
Symbolite is designed to facilitate the easy integration of new backends.
